---
title: "R Notebook"
output: html_notebook
---
Import command: source(dataframe)

Dimensions: dim(dataframe)
  This will give the rows and columns of the data
  
Names of the Columns: names(dataframe)

To call a certain row/column, use (dataframe name)$(variable); without parentheses

  This can be avoided by first running "attach(dataframe name)"
  Attach sepeartes the column name from the data frame and is an easy way to refer to the variable name
  
  Ex:
  attach(dataframe)
  title1
  title2

This only calls the raw numbers and observations of the variables.

To plot information on a graph:

plot(x, y, type, color, etc.)
  type = p: scatterplot
  type = l: line chart
  
To get help on a function/method: place a  "?" in front of the call

Variables can also be added with one another:
  Ex:
  plot(year, boys+girls, type = "p") This will calculate the total amount of children in the given dataframe
  plot(year, boys/girls, type = "p") This will compare the number of boys to girls; value >1 means more boys than girls
  plot(year, boys/(girls+boys), type = "p") This will compare the proportion of boys to girls; larger numbers mean that there     are more boys than girls
  
To figure out the points where the two varaibels are equal, greater, less than, etc.
  (variable2) =, <, >, etc. (variable2)
  
Hashtags can change the types of text
    ##

T-Test/Confidence Intervals

ttestout = t.test(fresh, stred, alternative = 'two-tailed', var,equal = TRUE)

ttestout$conf.int

Default critical value is 0.05.

Is 0 in the confidence interval? If it is not, then it is possible to conclude that Ho is not true (u1 = u2 so u1 - u2 should equal 0)

May reject on a two-tailed test, but on a one-sided t-test, it can be different


```{r}
pt(3.956, 89, lower.tail= FALSE)
```


```{r}
qf(0.05, 3, 20, lower.tail = FALSE)
pf(4.85, 3, 20, ncp=0, lower.tail=FALSE)
help(qf)
```
```{r}
a = 25 * 156.25
b = 25 * 128.84
c = a+b
d = c/50
e = sqrt(d)
f = e * sqrt(1/13)
g = 3.7/f

qt(0.025, 50, lower.tail = FALSE)

pt(-1.117, 50)
2 *0.13467
```
```{r}
a = 3.6 + 0.27 + 0.29 + 4.55 + 2.6 + 2.29 + 2.4 + 0.73 + 3.15 + 3.21 + 0.88 + 1.35 + 7.35
b = a/13
c = 1.36 + 0 + 0 + 1.79 + 2.04 + 3.14 + 2.72 + 0.24 + 1.57 + 0.43 + 0.28 + 1.09 + 4.92
d = c/13
b - d
qt(0.05, 12, lower.tail = FALSE)
pt

2 * pf(2.214, 25, 25, lower.tail = FALSE)

pf(1.57, 11, 11, lower.tail = FALSE)

qf(0.05, 2, 25, lower.tail = FALSE)

pf(8.9, 2, 25, lower.tail = FALSE)

pf(1480.22, 4, 495, lower.tail = FALSE)

qf(0.025, 25, 25, lower.tail = FALSE)

pf(2.48, 11, 11, lower.tail = FALSE)

qf(0.01, 11, 11, lower.tail = FALSE)

qf(0.05, 11, 11, lower.tail = FALSE)

pf(9.26, 2, 26, lower.tail = FALSE)
```








```{r}
qf(.025, 7, 7, lower.tail = FALSE)
pf(5.87, 7, 7, lower.tail = FALSE)
```


```{r}
GPA = read.csv('GPA1.csv')
attach(GPA)
mean(GPA$Y)
sd(GPA$X)
GPA[order(GPA$X),]
GPA.fit <- lm(Y~X, data = GPA)
summary(GPA.fit)
qt(0.95, 118, lower.tail = FALSE)
qf(0.05, 2, 23)



```

```{r}
plastics = read.csv('Plastic.csv')
attach(plastics)
plastics.fit <- lm(Y~X, data = plastics)
summary(plastics.fit)
mean(plastics$X)

```


